Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems

### 2021-02-04 paper/main.tex
paper s5

\begin{figure*}[tb]
  \small
  \centering%
    \includegraphics[width=0.49\textwidth]{../img/fitness_lop_IO_N-t59b11xx}
    \includegraphics[width=0.49\textwidth]{../img/fitness_lop_SGB_N-sgb75_02}
\\
    \includegraphics[width=0.49\textwidth]{../img/fitness_lop_RandB_N-p40-01}
    \begin{minipage}{0.49\linewidth}
          \texttt{RandB N-p50-01} (LOP)\\[-0.5ex]
    \includegraphics[width=\textwidth]{../img/fitness_lop_RandB_N-p50-01}
  \end{minipage}
    \\
    \begin{minipage}{0.49\linewidth}
    \texttt{reC19} (PFSP)\\[-0.5ex]
\includegraphics[width=\textwidth]{../img/fitness_pfsp_rec19_txt}
\end{minipage}
\begin{minipage}{0.49\linewidth}
    \texttt{reC31} (PFSP)\\[-0.5ex]
    \includegraphics[width=\textwidth]{../img/fitness_pfsp_rec31_txt}
  \end{minipage}
\label{fig:results}
  \caption{Mean fitness  (and standard deviation)  of each solution evaluated by each algorithm on various instances.\label{fig:rec05}}
\end{figure*}

>>>>

\begin{figure*}[tb]
\small
\centering%
\begin{minipage}{0.49\linewidth}
  \texttt{N-t59b11xx} (LOP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{../img/fitness_lop_IO_N-t59b11xx}
\end{minipage}
\begin{minipage}{0.49\linewidth}
  \texttt{N-sgb75-01} (LOP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{../img/fitness_lop_SGB_N-sgb75_02}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
  \texttt{N-p40-01} (LOP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{../img/fitness_lop_RandB_N-p40-01}
\end{minipage}
\begin{minipage}{0.49\linewidth}
  \texttt{N-p50-01} (LOP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{../img/fitness_lop_RandB_N-p50-01}
\end{minipage}
\\
\begin{minipage}{0.49\linewidth}
  \texttt{reC19} (PFSP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{../img/fitness_pfsp_rec19_txt}
\end{minipage}
\begin{minipage}{0.49\linewidth}
  \texttt{reC31} (PFSP)\\[-0.5ex]
  \includegraphics[width=\textwidth]{../img/fitness_pfsp_rec31_txt}
\end{minipage}
\label{fig:results}
\caption{Mean fitness  (and standard deviation)  of each solution evaluated by each algorithm on various instances.\label{fig:results}}
\end{figure*}
